% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,12pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.30}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
	\textbf{{\huge Shi Jin}} & \href{mailto:js1421@uw.edu}{js1421@uw.edu}\\
&   \href{mailto:kingstone1991@gmail.com}{kingstone1991@gmail.com} \\
  & \Mobilefone{ $\mathnormal{+1}$ $\mathnormal{2066050419}$}\\
  { \footnotesize Address:  3910 15th Ave. NE. } & \\
  { \footnotesize Department of Physics, University of Washington }& \\
  { \footnotesize Seattle, WA, 98195} &
	\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%
\resheading{Education}	
\ressubheading{\href{http://www.uw.edu}{University of Washington (UW) }}{\hspace{7.7cm} Seattle, WA, USA}{\href{https://sharepoint.washington.edu/phys/Pages/default.aspx}{PhD in Physics}}{\hspace{7.5cm} 2018 (expected) }
			\begin{itemize}
			\itemsep0em
	\item
	\textit{Weiss Award},  Department of Physics, UW (2015)		 	  
	\item Research Assistant, 2014 - present; Teaching Assistant, 2013 - 2014.
        \end{itemize}

				
\ressubheading{\href{http://en.ustc.edu.cn}{University of Science and Technology of China (USTC) }}{\hspace{2.5cm} Hefei, Anhui, China}{\href{http://physics.ustc.edu.cn}{Bachelor of Science}}{\hspace{2.5cm} Jun. 2013}
				\begin{itemize}
				\item
				\textit{Excellent Graduates Award}, USTC (2013)
                        \item  
     \textit{Outstanding Students Award}, USTC (2010, 2011, 2012, 2013)
     \item
     Visiting student in {\href{http://www2.physics.ox.ac.uk/}{ Department of Physics, University of Oxford}} (Jul. -- Oct. 2012)
				\end{itemize}						
								
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%


\resheading{Publications}
\fontsize{10}{12}\selectfont

\begin{itemize}
\itemsep0em
\item
A. Bulgac and S. Jin, \textit{Dynamics of Fragmented Condensates and macroscopic entanglement},  \href{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.119.052501}{Phys. Rev. Lett. 119, 052501 (2017)}


\item
S. Jin, A. Bulgac, K. Roche and G.Wlaz\l{}owski, \textit{Coordinate-Space Solver for Superfluid Many-Fermion Systems with Shifted Conjugate Orthogonal Conjugate Gradient Method}, \href{https://journals.aps.org/prc/abstract/10.1103/PhysRevC.95.044302}{Phys. Rev. C 95, 044302 (2017)}

\item
J. Grineviciute, P. Magierski, A. Bulgac, S. Jin and I. Stetcu, \textit{Accuracy of fission dynamics within the time dependent superfluid local density approximation}, \href{https://arxiv.org/abs/1711.02169}{Proceedings of XXXV Mazurian Lakes Conference on Physics, Piaski, Poland, September 3-9, 2017}

\item
A. Bulgac, M. M. Forbes, S. Jin, R. Navarro Perez and N. Schunck, \textit{A Minimal Nuclear Energy Density Functional}, \href{https://arxiv.org/abs/1708.08771}{arXiv: 1708.08771}

\item
A. Bulgac, S. Jin, P. Magierski, K.J. Roche, N. Schunck, and I. Stetcu, \textit{Nuclear Fission: from more phenomenology and adjusted parameters to more fundamental theory and increased predictive power }, \href{https://www.epj-conferences.org/articles/epjconf/abs/2017/32/epjconf_fusion2017_00007/epjconf_fusion2017_00007.html}{ The FUSION17 conference, Hobart, Australia, Feb. 20-24, 2017}

\item
A. Bulgac, S. Jin, P. Magierski, K.J. Roche, and I. Stetcu, \textit{Microscopic theory of nuclear fission}, \href{https://pos.sissa.it/cgi-bin/reader/contribution.cgi?id=281/225}{PoS(INPC2016)225, the 26th International Nuclear Physics Conference, Adelaide, Australia, Sep. 11-16, 2016}

\item
A. Bulgac, S. Jin, P. Magierski, K.J. Roche, and I. Stetcu, \textit{Induced fission of $^{240}$Pu}, \href{https://arxiv.org/abs/1702.08490}{the 6th International Conference on Fission and Properties of Neutron-Rich Nuclei, Sanibel Island, FL, Nov. 6-12, 2016}


\item
A. Bulgac, M.M. Forbes, and S. Jin, \textit{Nuclear density functionals: what do we really know?} \href{http://arxiv.org/abs/1506.09195}{ arXiv:1506.09195}

\end{itemize}

\resheading{Talks and Posters} 
\fontsize{10}{12}\selectfont

\begin{itemize}
\itemsep0em
\item
LANL FIESTA Fission School \& Workshop, Sep. 17-22, 2017,   Santa Fe, NM, USA

Poster: \textit{Induced fission of $^{240}$Pu within time-dependent density functional theory.}

\item
APS Northwestern Section Meeting, May 14-16, 2015,   Pullman, WA, USA

Talk: \textit{Shifted Conjugate-Orthogonal Conjugate-Gradient (COCG) method in Nuclear Physics}


\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%


     
\end{document}



